Re-Allocation of Resources during Releases \titlenote{Copyright note}

### 2013-11-22 paper1/paper1.tex
updating paper and new scripts for reports

In the early 1990's the Linux kernel development was not so busy affair \cite{linux_kernel}. There were very small number of users and developers involved at that time. Developers use a loosely time-based release process. Linux publishes it's major kernel release in every two or three months. If we look at figure 2 the Release Duration Line represents how the stable releases are going on since 2005. From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days.

@@

@@

We found that there was not a great number of people contributing during the time of merge periods. The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers . In figure 3 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 4.

@@

Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ MP and RDP). To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
\begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}
The Jaccard Distance can be obtained by subtracting the Jaccard Coefficient from 1.
\begin{equation} d_j(A, B) = 1 - J(A, B) = \frac{|A \cup B|-|A \cap B|}{|A \cup B|} \end{equation}
Here A and B are two sets. For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release. If set A is the set of files worked in MP and files worked for in another release is set B then In figure 5 the Jaccard distances between MP and RDP for each release can be represented. The average distance is 0.959 but the average distance after release ``linuxv2.6.39'' has gone up than the average up to this point. So we can say that developers work in very different areas once the merge window is closed and all core developments, feature developments, merging other branches regarding the previous release are done. Regarding the increase in the Jaccard Distance for the minor releases (since linuxv3.0) we can say that in minor releases developers work in more versatile areas than micro releases.

@@

\subsection{Developers' contributions around the time of release}
\textit{Do developers work on different areas of the system around the time of release?}\newline
\textit{How do developers own code around t he system?}

Developers work for the software continuously. Some are working for the core development some are working for the fixing and minor enhancements and some for feature developments, planning to merge new feature with any future release but we would like to understand what amount of changes they make during the time of regular development period and what amount the changes they make during the time of RTR. We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80% chruns in his lifetime.

We examine contribution in writing code and making churns. Figure 6 plots the representation of code churns and ownerships per developer.

>>>>

In the early 1990's the Linux kernel development was not so busy affair \cite{linux_kernel}. There were very small number of users and developers involved at that time. Developers use a loosely time-based release process. Linux publishes it's major kernel release in every two or three months. If we look at figure 2 the upper Line represents how the stable releases are going on since 2005. From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days. The bottom line which is much steady than the upper one is representing the durations of merge period in each stable release. If we put the releases in a time domain we can see a picture shown in figure 3 where we see that the stable releases are all going on maintaining almost a similar frequency and similar pattern. The highest picks are the merge periods then the smaller picks between the highest ones are representing the rc releases. For more clear view we have plotted only 100 releases of all 340 releases.

@@

\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3.4in]{relTimeDomain100.png}
\caption{\small \sl Time Domain for Releases}
\end{center}
\end{figure}

@@

We found that there was not a great number of people contributing during the time of merge periods. The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers . In figure 4 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 5.

@@

Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ MP and RDP). To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
\begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}
The Jaccard Distance can be obtained by subtracting the Jaccard Coefficient from 1.
\begin{equation} d_j(A, B) = 1 - J(A, B) = \frac{|A \cup B|-|A \cap B|}{|A \cup B|} \end{equation}
Here A and B are two sets. For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release. If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between MP and RDP for each release can be represented. The average distance is 0.959 but the average distance after release ``linuxv2.6.39'' has gone up than the average up to this point. So we can say that developers work in very different areas once the merge window is closed and all core developments, feature developments, merging other branches regarding the previous release are done. Regarding the increase in the Jaccard Distance for the minor releases (since linuxv3.0) we can say that in minor releases developers work in more versatile areas than micro releases.

@@

\subsection{Developers' contributions around the time of release}
\textit{Do developers work on different areas of the system around the time of release?}\newline
\textit{How do developers own code around the system?}

We are supposed to find the answers for the two research questions together in this section. Developers work for the software continuously. Some are working for the core development some people are for the fixing and minor enhancements and some for feature developments, planning to merge new features with any up coming release but we would like to understand what number of files they change during the time of regular development period and how many during the time of RTR. How many of them they really own and how many files they work that they do not own. We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80% chruns in his lifetime.

Since the release of ``linuxv2.6.13'' till ``linuxv3.11'' 2889 developers out of 14621 worked for the files they owned. They have worked for other files also. So the percentage of working with owned files is 19.82% through out the life time (here 2.6.13 to 3.11).

We examine the contribution in writing code and making churns by the developers. Figure 7 plots the cumulative representation of code churns and ownerships per developer.
